\bf\mftitle

### 2011-01-31 doc/jInfer/architecture/architecture.tex
Documentation: TODOs in progress.

For even more generality in design, we decided to implement abstract classes in midlevel:
\begin{itemize}
	\item \code{AbstractNamedNode} which implements methods from \code{NamedNode} interface to handle context, name and metadata (will discuss later in section \ref{section_metadata}),
	\item \code{AbstractStructuralNode} which implements only the task of deciding if instance is \code{Element} or \code{SimpleData}.
\end{itemize}
As practice showed, for methods handling and infering structural properties, it is important to recognize whether structural node on input is element or text node. % TODO anti Unclear, rewrite
However methods for content devising don't need to know if they are working on infering model for content of attribute or text node. % TODO anti Unclear, rewrite

Finally, our interface/class model for representing XML nodes is drafted in fig. \ref{nodes}. Those who are brave enough can look at fig. \ref{nodes_full2}.
In result, \code{Element} and \code{SimpleData} have method \code{getType()} to devise type of \code{Abstr\.act\.Stru\.ctu\.ral\.Node} variables. % TODO anti What is "devise"?
And \code{SimpleData} and \code{Attribute} have methods \code{getContentType()} and \code{getContent()} to work with content model.
% TODO anti Last 2 sentences make no sense to me...

@@

Take care of symbol class and its \code{equals()} implementation. % TODO anti What does it mean, to take care?
Automaton uses \code{equals()} to compare symbols on transitions (when building prefix-tree automaton and when merging states).
If you are using strings, you're just fine. With complicated objects, the first option is to make sure that equivalent objects are properly tested in \code{equals()}.
Second, maybe faster solution is to cluster objects into classes of equivalence before inserting them into automaton.
Then give automaton only cluster representant object (which will use java \code{Object.equals()} with reference comparison) for each object encountered.

@@

One can ask for merging states, that are merged out from automaton already. % TODO anti What does it mean?
Lets take example automaton of fig. \ref{automaton_merge1} (states are labeled [name|finalCount], steps by \{symbol|useCount\}).
One asks to merge states 3 and 4.
State 3 then becomes final state with loop and state 4 disappears (fig. \ref{automaton_merge2}).
If then one asks to merge states 2 and 4, automaton properly handles situation by knowing, that old state 4, was merged into state 3, and merges states 2 and 3 (see fig. \ref{automaton_merge3}).
This can be useful in $k,h-context$ and $s,k-strings$ implementations (find all context/strings, then supply list of states to merge and don't bother with state names updates).

>>>>

For even more generality in design, we decided to implement abstract classes in midlevel:
\begin{itemize}
	\item \code{AbstractNamedNode} which implements methods from \code{NamedNode} interface to handle context, name and metadata (will discuss later in section \ref{section_metadata}),
	\item \code{AbstractStructuralNode} which implements only the task of deciding if instance is \code{Element} or \code{SimpleData}.
\end{itemize}
% TODO vektor Na jednej strane nas zaujima struktura, na to tam mame isElement() isSimpleData(), na druhej strane nas zaujimaju textove data, na to tam mame getContent() v SD aj atribute.

Finally, our interface/class model for representing XML nodes is drafted in fig. \ref{nodes}. Those who are brave enough can look at fig. \ref{nodes_full2}.

@@

Automaton uses \code{equals()} to compare symbols on transitions (when building prefix-tree automaton and when merging states).
If you are using strings, you're just fine. With complicated objects, the first option is to make sure that equivalent objects are properly tested in \code{equals()}.
Second, maybe faster solution is to cluster objects into classes of equivalence before inserting them into automaton.
Then give automaton only cluster representant object (which will use java \code{Object.equals()} with reference comparison) for each object encountered.

@@

% TODO vito Aby bolo mozne odkazovat sa na uz zmergovane stavy, ktore sa uz volaju inak, pouzivame mapu premenovani.
Lets take example automaton of fig. \ref{automaton_merge1} (states are labeled [name|finalCount], steps by \{symbol|useCount\}).
One asks to merge states 3 and 4.
State 3 then becomes final state with loop and state 4 disappears (fig. \ref{automaton_merge2}).
If then one asks to merge states 2 and 4, automaton properly handles situation by knowing, that old state 4, was merged into state 3, and merges states 2 and 3 (see fig. \ref{automaton_merge3}).
This can be useful in $k,h-context$ and $s,k-strings$ implementations (find all context/strings, then supply list of states to merge and don't bother with state names updates).
